---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# qdrant

<!-- badges: start -->
<!-- badges: end -->

The goal of qdrant is to ...

## Installation

You can install the development version of qdrant from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("thisisnic/qdrant")
```

## Example

Let's take a look at populating an in-memory vector database and then searching it.

We start by setting up the data we want to use in our analysis.

```{r example}
library(reticulate)
reticulate::use_virtualenv("r-qdrant_client")
devtools::load_all(".")

# Read the CSV file into a data frame
df <- read.csv(system.file("top_rated_wines.csv", package="qdrant"))

# Remove any rows where 'variety' is NA
df <- df[!is.na(df$variety), ]

# Randomly sample 700 rows
set.seed(123) # Set seed for reproducibility, if needed
sampled_indices <- sample(1:nrow(df), 700)
data <- df[sampled_indices, ]
```

Next, we create the user prompt we want to use to search the data

```{r}
user_prompt <- "A wine from Mendoza Argentina"
```

Then we encode both the data and user prompt - here I'm using the Python `sentence_transformers` library to do this.

```{r}
# set up encoder
st <- import("sentence_transformers")
encoder <- st$SentenceTransformer('all-MiniLM-L6-v2')
embedding_size <- encoder$get_sentence_embedding_dimension()

# encode input data and user prompt
encoded_data <- construct_points(data, encoder)

# Encode user prompt
encoded_prompt <- encoder$encode(user_prompt)
```

Now we initialise a new qdrant instance in memory

```{r}
r_qdrant <- qdrant(":memory:")
```

We initialise the collection with our data

```{r}
create_collection(
  r_qdrant,
  "top_wines", 
  vectors_config = vector_params(size = embedding_size, distance = "Cosine")
)
```

We then upload our data to the collection

```{r}
upload_points(r_qdrant, "top_wines", encoded_data)
```

And now we can search our collection using the encoded prompt!

```{r}
results <- search(r_qdrant, "top_wines", encoded_prompt, limit=3L)
for(result in results){
  cat(paste("Score:", round(result$score, 2)), fill = TRUE)
  cat(paste("Wine:", result$payload$name), fill = TRUE)
  cat(paste("Region:", result$payload$region), fill = TRUE)
  cat(paste("Notes:", result$payload$notes), fill = TRUE)
  cat("", fill = TRUE)
}
```
